Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-12 paper/us_election_2020.qmd
more changes in methodology

## Features
The original CES 2020 dataset, which shows in @tbl-raw, contains 61000 observations and 5 variables, which are "votereg", "CC20_410", "race", "region", "employ".

@@

2. CC20_410: the person that respondent vote for President of the United States.

@@

## Methodology
Since it is difficult to observe through 61000 rows with 5 variables, this report will only explore and analyze through specific aspects. The original dataset contains respondent's voter registration status and the person that respondent vote for President of the United States. This paper will only analyze respondents who are registered to vote and focus on only two voting options, Biden and Trump.

>>>>

The transformation of real-world phenomena into quantifiable data points in our dataset is influenced by various factors, leading to inherent limitations in our measurements for our variables: "votereg", ", and political affiliation.

## Features
The original CES 2020 dataset, which shows in @tbl-raw, contains 61000 observations and many variables. We chose to feature these 5 variables: "votereg", "CC20_410", "race", "region", "employ", in our analysis.

@@

2. CC20_410: the presidential candidate the respondent voted for.

@@

## Methodology
Since it is difficult to observe such as large dataset, this report will only explore and analyze through specific aspects. The original dataset contains respondent's voter registration status and the presidential candidate the respondent voted for. This paper will only analyze respondents who are registered to vote and focus on the outcome of two candidates, Joe Biden representing the Democratic party and Donald Trump representing the Republican party.
